Contracts for Contracts

### 2023-04-26 paper.tex
some fix in code snippets

\begin{lstlisting}[language=Solidity]
  # {x | x > 0}
  # {y | y > x + 1}
  function f(uint x) returns y { ... }
\end{lstlisting}
It is also equivalent to core syntax:
\begin{lstlisting}
  # {x | x > 0} -> {y | y > x + 1}
\end{lstlisting}

@@

\begin{lstlisting}[language=Solidity]
  # {x | x > 0}
  function f(uint x) returns y { ... }
\end{lstlisting}
It is equivalent to core syntax where the omitted part is simply \code{true}:

@@

For multi-argument functions, we use multiple \code{->} to compose larger function
contracts:
\begin{lstlisting}
  # {x | x > 0} -> {y | y < 100} -> {z | z == x + y }
  function f(int x, int y) returns (int) { returns x + y; }
\end{lstlisting}
Or, we could write a single flat contract for the argument introducing
multiple argument binders:
\begin{lstlisting}
  # { (x, y) | x > 0 && y < 100 } -> {z | z == x + y }
  function f(int x, int y) returns int { returns x + y; }
\end{lstlisting}

@@

@@

\begin{lstlisting}
  # { a | { {value, gas}(arg) | <pre-cond> } -> { (res, data) | <post-cond> } }
  function f(address a) returns address { return a }
\end{lstlisting}

>>>>

\begin{lstlisting}[language=Solidity]
  # {x | x > 0}
  # {y | y > x + 1}
  function f(uint x) returns (uint y) { ... }
\end{lstlisting}
It is also equivalent to core syntax:
\begin{lstlisting}
  # {x | x > 0} -> {y | y > x + 1}
\end{lstlisting}

@@

\begin{lstlisting}[language=Solidity]
  # {x | x > 0}
  function f(uint x) returns (uint y) { ... }
\end{lstlisting}
It is equivalent to core syntax where the omitted part is simply \code{true}:

@@

For multi-argument functions, we use multiple \code{->} to compose larger function
contracts:
\begin{lstlisting}
  # {x | x > 0} -> {y | y < 100} -> {z | z == x + y }
  function f(int x, int y) returns (int z) { returns x + y; }
\end{lstlisting}
Or, we could write a single flat contract for the argument introducing
multiple argument binders:
\begin{lstlisting}
  # { (x, y) | x > 0 && y < 100 } -> {z | z == x + y }
  function f(int x, int y) returns (int z) { returns x + y; }
\end{lstlisting}

@@

\wac{We may need an example here since the necessity to designate the callee function may not be obvious to reviewers.}

@@

\begin{lstlisting}
  # { a | { {value, gas}(arg) | <pre-cond> } -> { (res, data) | <post-cond> } }
  function f(address a) returns (address) { return a }
\end{lstlisting}
